Fermi and eROSITA bubbles: A proof-of-concept study

### 2021-12-19 paper.tex
update

\begin{document}
\title{Fermi and eROSITA bubbles: a proof of concept study}

@@

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  the steady-state gaseous density distribution of disk and atmosphere\
  confined in the total potential, $\Phi_{\text{total}}$,\
  can be written as
  \begin{equation}
     \rho(z)=
     \begin{cases}
     \displaystyle\rho_{\text{disk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{disk}}/m_{\text{p}}}\right] & \text{, if $|z| < z_{0}$}\\
     \\
     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right] & \text{, otherwise,}
     \end{cases}
  \end{equation}
  where $m_{\text{p}}$ is a proton mass,\
  $T_{\text{disk}}$ and $T_{\text{atmp}}$ is the temperature of the disk and the atmosphere,\
  $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
  of the bulge and atmosphere on the mid-plane $z=0$.

  All parameters are listed in \Cref{table-parameters}, excpet for $\rho_{\text{atmp}}^{\text{peak}}$ that\
  can be derived from the known parameters and pressure equilibrium\
  on the interfaces $(z=\pm z_{0})$ between disk and atmosphere.

>>>>

\begin{document}
\title{Fermi and eROSITA bubbles: A proof-of-concept study}

@@

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  we can write the steady-state gaseous density distributions of disk and atmosphere\
  that are in pressure equilibrium and\
  confined in the total potential, $\Phi_{\text{total}}$, as\
  \begin{equation}
     \rho(z)=
     \begin{cases}
     \displaystyle\rho_{\text{disk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{disk}}/m_{\text{p}}}\right] & \text{, if $|z| < z_{0}$}\\
     \\
     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right] & \text{, otherwise,}
     \end{cases}
  \end{equation}
  where $m_{\text{p}}$ is a proton mass,\
  $T_{\text{disk}}$ and $T_{\text{atmp}}$ is the temperature of the disk and the atmosphere,\
  $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
  of the disk and atmosphere on the mid-plane $z=0$.

  All parameters are listed in \Cref{table-parameters}, except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
  can be derived from the known parameters and pressure equilibrium condition\
  on the interfaces $(z=\pm z_{0})$ between disk and atmosphere.
